### 2014-07-14 Quality_Reports/PCR_bottleneck.Rmd
Change calculation of PCR to use spp package

```{r PBC_fun,include = TRUE,results = "hide",echo = TRUE}
PBC <- function(file,cap = Inf)
{
  require(GenomicAlignments)
  message(file)
  rr = readGAlignmentsFromBam(file,param = NULL)
  ss1 = subset(rr,subset =strand(rr)=="+")
  ss2 = subset(rr,subset = strand(rr)=="-")
  tab1 = table(start(ss1))
  tab2 = table(end(ss2))
  tab = table(c(start(ss1),end(ss2)))
  PBC1 = round(sum(tab1 == 1)/sum(tab1 >= 1 & tab1 <= cap),4)
  PBC2 = round(sum(tab2 == 1)/sum(tab2 >= 1 & tab2 <= cap),4)
  PBC = round(sum(tab == 1) / sum(tab >= 1 & tab <= 4),4)
  message("PBC +:",PBC1)
  message("PBC -:",PBC2)
  message("PBC:",PBC)
  return(c(PBC_plus=PBC1,PBC_minus=PBC2,PBC=PBC))  
}
```

>>>>

```{r PBC_fun,include = TRUE,results = "hide",echo = TRUE}
PBC <- function(file,cap = Inf)
{
  require(GenomicAlignments)
  require(spp)
  message(file)
  rr = readGAlignmentsFromBam(file,param = NULL)
  ss1 = subset(rr,subset =strand(rr)=="+")
  ss2 = subset(rr,subset = strand(rr)=="-")
  tab1 = table(start(ss1))
  tab2 = table(end(ss2))
  tab = table(c(start(ss1),end(ss2)))
  PBC1 = round(sum(tab1 == 1)/sum(tab1 >= 1 & tab1 <= cap),4)
  PBC2 = round(sum(tab2 == 1)/sum(tab2 >= 1 & tab2 <= cap),4)
  chip.data = read.bam.tags(file)
  table.chip.data = lapply(chip.data$tags,table)
  nUniq = sum(sapply(table.chip.data,function(x) sum(x==1)))
  nTotal =  sum(sapply(table.chip.data,length))
  PBC = round(nUniq/nTotal ,4)
  message("PBC +:",PBC1)
  message("PBC -:",PBC2)
  message("PBC:",PBC)
  return(c(PBC_plus=PBC1,PBC_minus=PBC2,PBC=PBC))  
}
```
